Methodology for Assessing the State of the Practice for Domain X

### 2020-09-21 StateOfPractice/Methodology/Methodology.tex
updated section 7 of Methodology doc

\section{Domain Analysis} \label{SecDomainAnalysis}
The domain analysis consists of a commonality analysis of the software packages. Its purpose is to show the relationships between these packages, and to facilitate an understanding of the informal specification and development of them. The final result of the analysis will be tables of commonalities, variabilities and parameters of variation.

\noindent Steps to produce a commonality analysis:
\begin{enumerate}
\item Write an Introduction
\item Write the Overview of Domain
\item List Commonalities - Split into sections for the simulation step, input information, output information, and nonfunctional requirements
\item List Variabilities - Split into sections for the simulation step, input information, output information, and nonfunctional requirements
\item List Parameters of Variation - Split into sections for the simulation step, input information, output information, system constraints, and nonfunctional requirements
\item Add Terminology, Definitions, Acronyms
\end{enumerate}

>>>>

\section{Domain Analysis} \label{SecDomainAnalysis}
\pmi{SS:"We should have more of an introduction on what is a commonality analysis, and more generally, what is a program family. We should also have more of a literature review, and a pointer to examples. Some publications to look at include ArdisAndWeiss1997, Chen2003, SmithAndChen2004, SmithEtAl2008, SmithMcCutchanAndCarette2017, Weiss1998"}
The domain analysis consists of a commonality analysis of the software packages. Its purpose is to show the relationships between these packages, and to facilitate an understanding of the informal specification and development of them. The final result of the analysis will be tables of commonalities, variabilities and parameters of variation.

\noindent Steps to produce a commonality analysis:
\begin{enumerate}
\item Write an Introduction
\item Write the Overview of Domain
\item List Commonalities
\item List Variabilities
\item List Parameters of Variation
\item Add Terminology, Definitions, Acronyms
\end{enumerate}
